Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-31 paper/paper.tex
table 5

>>>>

\renewcommand{\arraystretch}{0.9}
\begin{table*}[t!]
  \footnotesize
  \caption{\label{table:attacks}-}
  \vspace{-2ex}
  \centering
    \begin{tabular}{lp{2cm}p{2.1cm}ccp{2cm}c}
    \toprule
    \multicolumn{1}{c}{Paper} &
    \multicolumn{1}{c}{Input} &
    \multicolumn{1}{c}{Dataset} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Output} &
    \multicolumn{1}{c}{Evaluation} &
    \multicolumn{1}{c}{Availability} \\
    \midrule
    \cite{vollmer-etal-cics2011} & Malign Traffic & Manually crafted & ICMP & Rule List & TP, FP & No\\
    \midrule
    \cite{fallahi} & Mixed Traffic & \cite{iscx} & HTTP, SSH, TCP & Single Rule & TP, FP, Precision, Recall, F1 & No\\    
    \midrule
    \cite{Kao2015AutomaticNR} & Malign Traffic, Benign Traffic, Rule Dataset & Manually crafted, \cite{emerging-threats-open} & HTTP & Single Rule & Generating time, FP & No \\
    \midrule
    \cite{guruprasad}& Malign Traffic & \cite{iscx} \cite{darpa1999} & ICMP, TCP & Rule List & FP & No\\
    \midrule
    Syrius & Malign Traffic, Benign Traffic, Rule Dataset & Manually crafted, \cite{emerging-threats-open}, \cite{iscx} & HTTP, TCP, ICMP & Rule List & Rule Ranking & Yes \\
    \bottomrule
  \end{tabular}
\end{table*}
